Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-05-06 ForegroundSimulations/reply_to_referee_report.txt

Response: I have noted in section 5.1 that foreground contamination depends on baseline length, orientation, pointing direction and spatial structure of emitting source. Hence, I chose a range of baseline lengths and orientations. I used all unique baseline lengths to demonstrate that all baselines individually will be sensitive to the EoR signal. Figures 2 and 5 are now renumbered as 4 and 7 respectively.

Minor comments:

Abstract:
1) "with high significance": this sounds vague. Is there a sigma value or a signal-to-noise ratio (SNR) to quote?

Response: Unless thermal noise is included it is hard to quote a SNR. Here I have assumed data is not thermal noise limited but only limited by foregrounds and systematics studied in this paper. In such a scenario the significance of detection again varies anywhere from 10 to more than 1000. The exact detection significance will depend on the analysis methods and weighting schemes used.

@@

2) "strike an optimal balance between sensitivity and systematics": this is directly related to my major comments #1. First of all, even if that were the case, it is not quite appropriate to state it as a matter of fact in the introduction, since it is what this work is setting out to prove. Secondly, it seems clear in this work that the dish design has not truly achieved the optimum. Sections 5.2.1 and 5.2.2 explicitly state that 'measurements are under way" and "the HERA collaboration constantly pursues improvement of its dish design".

Response: Removed the word "optimal". The balance between sensitivity and systematics was initially studied in DeBoer and Parsons (2015) - a HERA memo - to which a citation has now been added. This study was specific to choice of dish size and preliminary estimates of specifications for dish based on sensitivity and systematics. Our current work along with companion papers are a much more comprehensive effort to further reinforce findings of that preliminary study. It is in this context that sentence was used. Unlike the dish design, it is true that the feed design is not finalized yet and is still being fine-tuned for optimum performance. Hence, removal of the word "optimum" is consistent with other statements about measurements and fine-tuning of the HERA element (dish and feed together) design.

3) I think it is never explained in this section that HERA 19 is already built, and full HERA with 320 elements is being proposed?

Response: The last paragraph in section 2 mentions this. A figure (now numbered 1) has been introduced to show the actual HERA-19 layout built on site.

@@

Section 4:
1) It would be helpful to explain in half a sentence what kind of software HFSS is. Is it a commercial simulation software, or a customized HERA software?

Response: Added a brief description

2) The authors go into great detail as to what the materials are used in simulation, which leaves the reader wondering: are they the same as what are actually used in the dish? For example, "the backplane is modeled as an aluminum surface", but is it actually an aluminum surface? A nice picture of an actual HERA dish may help here.

Response: A picture has been added (now figure 2). The dipoles are modeled using the actual materials used. The dish and backplane are made of meshed surfaces which are computationally hard to model with HFSS. Instead they have been modeled as aluminum surfaces. At these frequencies, the cross-welded mesh electrical properties are well modeled as a good conductor like aluminum. A paragraph has been added in section 4.1 that describes these details.

@@

Section 5:
1) "The equation for delay spectrum": explicit \eqref (that is, identify the equation)

Response: Explicitly refer to equations 1 and 2 as suggested

2) "by convolving a Blackman-Harris window with itself": I might be wrong here, but Fig. 1 looks like a multiplication in frequency and convolution in delay domain? If it is squared in the delay domain, where do the ripples come from in the BH*BH curve in the delay domain since the BH curve is smooth?

Response: It is definitely a multiplication in delay domain as equation 10 indicates. This is what leads to the squaring and increase in dynamic range in delay domain. However, it is not a squaring of the same exact BH delay domain curve (gray) shown in the bottom of figure 1 (now fig. 3). This is because after convolving in frequency the resultant window must fit in a 100 MHz band end-to-end. An auto-convolution of the BH curve shown in the figure (which already already occupies 100 MHz end-to-end) will result in a curve that takes up 200 MHz end-to-end. Hence a new BH curve with appropriate width is chosen such that after auto-convolution, the resultant curve occupies 100 MHz. In other words, the black curve in top panel is not obtained by convolving gray curve with itself but from a slightly different BH curve of different (smaller) width with itself. This is the reason the null-like dips in delay domain are not aligned between the two. I have added a few sentences to describe this subtlety.

@@

The ripples seen could be because of the aforementioned adjustments in frequency domain. Also being at the level of 10**-8 to 10**-5 they are insignificant compared to the overall dynamic range. In other words, even if the gray curve had ripples at this level, in a log scale plot they will not appear as ripples when superimposed on the tail which is at the level of 10 to 10**4. Thus it will not be surprising that the gray curve will still appear smooth despite these ripples.

3) If the square of the Blackman-Harris window works so much better, why not the third or fourth power?

Response: With higher order powers of the delay domain response, they start getting broader in delay and narrower in frequency. This results in loss of thermal noise senstivity due to loss of effective bandwidth. And viewing from a Fourier domain perspective, due to loss of delay resolution, sensitivity to large scale structure will reduce slightly. In conclusion, it is possible to use higher order powers but depending on the application, this may result in loss of sensitivity especially on large scales. In this paper, we found that squaring was sufficient to achieve the dynamic range required for our purposes. I have added a small note highlighting this trade-off.

@@

4) Fig 1: the axis labels for the top plot have non math mode fonts, which are inconsistent with all other plots.

Response: Corrected as suggested. Now figure 3.

5) Fig 1: 'as a result' is a strange transition since the previous sentence is talking about epsilon.

Response: Removed the phrase "As a result" in what is now figure 3.

@@

Section 6:
1) The transition between sections 5 and 6 can use a few more sentences. It is not very clear how the dynamic range relates to the dish's reflectometry.

Response: Added a transition sentence at the beginning of the first paragraph in section 6.

2) Fig. 6: comment on the dark stripe around RA hour 17?

Response: The last paragraph in section 6 discusses this. I have also added a sentence describing it in the caption of figure (now #8).

### 2016-05-06 ForegroundSimulations/ms.tex
Address referee comment on HFSS modeling details
From 83d99a7 (fgsim):
====================

(*) Add hera19.eps and hfssHERA.eps to git repo

In ms.tex,

(*) Address referee comment on HFSS modeling details
(*) Include HERA-19 layout and HFSS schematic figures with
corresponding texts

In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that {\bf is} currently in use. Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.

@@

The High Frequency Structural Simulator (HFSS), {\bf a commercial finite element method solver for electromagnetic structures from Ansys,} was used to model the dish and its angular response used in this study. The HFSS model used prime focus optics with a 14~m faceted parabola with a spar f/D ratio of 0.32.  The model has a 1~m central hole in the aluminum surface which is filled with a dielectric material similar to dry soil. The feed used a full PAPER dipole inside of a cylindrical backplane, the backplane is modeled as an aluminum surface. For the metal parts of the dipole, the discs were modeled as aluminum at the actual size, and the arms and terminals were modeled as copper. Dielectric stand-offs and supporting members were included. For the calculations, one pair of arms was excited using a modal port. These models cover a frequency range of 90--210~MHz in intervals of 1~MHz {\bf and include multiple reflections between the dish and the feed but not those between dishes} \citep{deb16}.

>>>>

In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that {\bf is} currently in use {\bf (see Figure~\ref{fig:HERA-19})}. Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{hera19.eps}
  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed layout. It is located in the South African Karoo Radio Astronomy Reserve.}}
  \label{fig:HERA-19}
\end{figure}

@@

The High Frequency Structural Simulator (HFSS), {\bf a commercial finite element method solver for electromagnetic structures from Ansys,} was used to model the dish and its angular response used in this study. The HFSS model used prime focus optics with a 14~m faceted parabola with a spar $f/D$ ratio of 0.32.  The model has a 1~m central hole in the surface which is filled with a dielectric material similar to dry soil. The feed used a full PAPER dipole inside a cylindrical backplane. Dielectric stand-offs and supporting members were included. For the calculations, one pair of arms was excited using a modal port.

{\bf The dipoles were modeled with the actual materials used -- aluminum for the discs and copper for the arms and terminals. The dish and the backplane are actually meshed surfaces. For computational feasibility, they were modeled as aluminum surfaces in HFSS. At these frequencies, the cross-welded mesh electrical properties are well modeled as a good conductor like aluminum.}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{hfssHERA.eps}
  \caption{{\bf Schematic representation of the HERA dish-feed assembly used in the HFSS model. The dish surface is modeled as a 14~m faceted parabola. The feed uses a PAPER dipole surrounded by a cylindrical backplane. A $f/D$ ratio of 0.32 is used. A length scale of 200~inches ($\approx 5$~m) is shown at the bottom for reference.}}
  \label{fig:HFSS-HERA}
\end{figure}

These models cover a frequency range of 90--210~MHz in intervals of 1~MHz {\bf and include multiple reflections between the dish and the feed but not those between dishes} \citep{deb16}.
